\sysfull

### 2018-08-07 paper/asplos19/systemdescription.tex
revisions of system description
minor change

\paragraph{Programming and Execution Model.}
To use \sys, a programmer must (i) convert a plain C code into tasks by encapsulating the code in a top-level set of functions, (ii) sequence the control-flow between these tasks, and (iii) annotate memory accesses that manipulate task-shared data. Then, they compile and link the code against \sys's runtime, producing a \sys-enabled binary. The runtime relies on \sys's novel {\em adaptive task scheduler} to adapt its execution with the energy conditions. Facilitating efficient task adaptation requires dynamic memory protection which \sys's \emph{virtual memory manager} handles through a process we call \emph{dynamic page privatization}.

@@

\paragraph{Virtual Memory Manager.}
\sys can coalesce tasks thanks to its virtual memory manager (VMM). VMM privatizes memory pages demanded by a coalesced task and limits application accesses only to the fast volatile memory. VMM keeps all page modifications in non-volatile memory on a coalesced task transition. Section~\ref{sec:memory_virtulaization} outlines VMM.

>>>>

\paragraph{Programming and Execution Model.}
To use \sys, a programmer must (i) convert a plain C code into tasks by encapsulating the code in a top-level set of functions, (ii) sequence the control-flow between these tasks, and (iii) annotate memory accesses that manipulate task-shared data. Then, they compile and link the code against \sys's runtime, producing a \sys-enabled binary. The runtime relies on \sys's novel {\em adaptive task scheduler} to adapt its execution with the energy conditions. Facilitating efficient task adaptation requires dynamic memory protection which \sys's \emph{virtual memory manager} handles through \emph{page privatization}.

@@

\paragraph{Virtual Memory Manager.}
\sys can coalesce tasks thanks to its virtual memory manager (VMM). VMM privatizes memory pages demanded by a coalesced task and limits application accesses only to the fast volatile memory. VMM keeps all page modifications in non-volatile memory on a coalesced task transition. VMM also solves a novel data consistency problem we call \emph{coalescing-induced WAR dependency}. Section~\ref{sec:memory_virtulaization} outlines VMM.
